Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-19 paper/ms.tex
minor

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II:
  A Validated Jupiter-Sized Planet in IC~2602
}

@@

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern: they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data render such scenarios highly
  unlikely.  Multi-color photometry requires eclipsing companions to
  have nearly identical color as TOI$\,$837, eliminating hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios
  are limited by speckle imaging, but formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further analysis of its mass, atmosphere, and obliquity
  should confirm its planetary nature beyond doubt, and will improve
  our understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602
}

@@

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern: they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Multi-color photometry requires eclipsing
  companions to have nearly identical color as TOI$\,$837, ruling out
  hierarchical eclipsing binary scenarios.  Background eclipsing
  binary scenarios are limited by speckle imaging, but formally remain
  a 0.2\% possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}
